A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-14 PPSN2016/paper.Rnw
Reviewing State of the Art.

In general, those papers go no further than a proof of concept,
attempting to gauge how many users join the effort and also how long
would it take a concrete amount of users to reach the solution. In
general, they do not try to assess the performance of the algorithm
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation so no actual contribution to the evaluation of the
evolutionary algorithm itself is made.

There is another factor that should be taken into account: since the
user has control of the browser, there is a limited amount of
interaction with it, namely, the fact that by reloading the webpage he
can apply a kind of hypermutation killing the current population and
generating new individuals some of which will make their way to the
common pool via migration. In that sense, volunteer computing is also
a way of {\em human computation} \cite{quinn2011human}, a concept that
has also been applied to evolutionary algorithms \cite{972056}, in
this case extensively and with all operators. It is quite difficult to
find out how many times this happens and what is their effect on the
overall algorithm, but this only reaffirms the fact that there is a
long list of issues with volunteer evolutionary computation, and that
the volunteer him or herself is at the center of many of them.

>>>>

In general, those papers go no further than a proof of concept,
attempting to gauge how many users join the effort and also how long
would it take for a concrete amount of users to reach the solution. In
general, they do not try to assess the performance of the algorithm
itself in the precise conditions they find in a volunteer computing
system, although papers such as the one by Laredo et
al. \cite{churn08:ijhpsa}, using models, try to find out the resulting
performance when the users are changing continously according to a
Weibull distribution. In the case of Klein and Spector \cite{unwitting-ec}, the algorithm
is actually run on the server, using the browser mainly for fitness
evaluation so no actual contribution to the evaluation of the
evolutionary algorithm itself is made.

There is another factor that should be taken into account: since the
user has control of the browser, there is a limited amount of
interaction with it, namely, the fact that by reloading the webpage they
can apply a kind of hypermutation, killing the current population and
generating new individuals some of which will make their way to the
common pool via migration. In that sense, volunteer computing is also
a way of {\em human computation} \cite{quinn2011human}, a concept that
has also been applied to evolutionary algorithms \cite{972056}, in
this case extensively and with all operators. It is quite difficult to
find out how many times this happens and what is their effect on the
overall algorithm, but this only reaffirms the fact that there is a
long list of issues with volunteer evolutionary computation, and that
the volunteer him or herself is at the center of many of them.
